\newpage
\begin{thebibliography}{99}

\bibitem{Crossfire}
M. S. Kang, S. B. Lee, and V. D. Gligor,
“The crossfire attack,”
in Proc. IEEE Symp. on Security and Privacy,
May 2013, pp. 127-–141.

\bibitem{ddossurvey01}
J. Mirkovic and R. Peter,
"A taxonomy of DDoS attack and DDoS defense mechanisms,"
ACM SIGCOMM Computer Communication Review, vol. 34(2), pp. 39--53, 2004.

\bibitem{ddossurvey02}
G. Carl, G. Kesidis, R. Brooks and S. Ray,
"Denial-of-service attack-detection techniques,"
IEEE Internet Computing, vol. 10(1), pp. 82--89, 2006.

\bibitem{ddossurvey03}
T. Peng, L. Christopher and R. Kotagiri,
"Survey of network-based defense mechanisms countering the DoS and DDoS problems,"
ACM Computing Surveys (CSUR), vol. 39(1), no. 3, 2007.

\bibitem{ddossurvey04}
H. Beitollahi and G. Deconinck,
“Analyzing well-known countermeasures against distributed denial of service attacks,”
Computer Communications,
vol. 35(11), pp. 1312–-1332, 2012.

\bibitem{ddossurvey05}
S. T. Zargar, J. Joshi, and D. Tipper,
“A survey of defense mechanisms against distributed denial of service (DDoS) flooding attacks,”
IEEE Communications Surveys \& Tutorials,
vol. 15, no. 4, 2013.

\bibitem{CoDef}
S. B. Lee, M. S. Kang, and V. D. Gligor,
“CoDef: collaborative defense against large-scale link-flooding attacks,”
in Proc. ACM CoNEXT,
December 2013, pp. 417-–428.

\bibitem{crossdomain}
D. Gkounis,
“Cross-domain DoS link-flooding attack detection and mitigation using SDN principles,”
Master’s thesis, Institute of Technology Zurich,
2014.

\bibitem{DetectTLFA}
L. Xue, X. Luo, E. W. W. Chan, and X. Zhan,
“Towards detecting target link flooding attack,”
in Proc. USENIX LISA,
November 2014.

\bibitem{as-relation}
AS Relationships. [Online]. Available: http://www.caida.org/data/asrelationships

\bibitem{AS1}
L. Gao,
“On inferring autonomous system relationships in the Internet,”
IEEE/ACM Transactions on Networking,
vol. 9, no. 6, pp. 733-–745, 2001.

\bibitem{AS2}
G. D. Battista, T. Erlebach, A. Hall, M. Patrignani, M. Pizzonia, and T. Schank,
“Computing the types of the relationships between autonomous systems,”
IEEE/ACM Transactions on networking, vol. 15,
no. 2, pp. 267-–280, 2007.

\bibitem{caballero2011measuring}
C. Juan, G. Chris, K. Christian and P. Vern,
"Measuring Pay-per-Install: The Commoditization of Malware Distribution,"
Usenix security symposium, 2011.

\bibitem{abu2006multifaceted}
M. Abu Rajab, J. Zarfoss, F. Monrose, and A. Terzis,
"A multifaceted approach to understanding the botnet phenomenon,"
in Proc. ACM SIGCOMM conference on Internet measurement,
ACM, 2006, pp. 41--52.

\bibitem{ldos1}
A. Kuzmanovic, and E. Knightly,
"Low-rate TCP-targeted denial of service attacks and counter strategies,"
IEEE/ACM Trans, on Networking, 14(5), Oct 2006.

\bibitem{ldos2}
Q. Zhu, Y. Zhang, and C. Xie,
"Research and survey of low-rate denial of service attacks,"
Advanced Communication Technology (ICACT), 2011 13th International Conference on,
pp. 1195--1198, 2011.

\bibitem{ldos3}
F. Yu, L. Gang, and C. Ming,
"The detection of low-rate denial-of-service attack based on feature extraction and analysis at congestion times,"
Electrical and Control Engineering (ICECE), 2011 International Conference on,
pp. 1338--1341, 2011.

\bibitem{ldos4}
K. Chen, L. Huiyu, and C. Xiaosu,
"EBDT: a method for detecting LDoS attack,"
Information and Automation (ICIA), 2012 International Conference on,
pp. 911--916, 2012.

\bibitem{ldos5}
C. Zhang, Z. Cai, W. Chen, X. Luo and J. Yin,
"Flowlevel detection and filtering of low-rate DDoS,"
Comput.Netw., vol. 56, no. 15, pp. 3417--3431, 2012.

\bibitem{ldos6}
F. Barbhuiya, V. Gupta, S. Biswas and S. Nandi,
"Detection and mitigation of induced low rate TCP-targeted denial of service attack,"
Software Security and Reliability (SERE), 2012 IEEE Sixth International Conference on,pp. 291--300, 2012.

\bibitem{agile}
F. Gillani, S. Lo, Q. Duan, M. Ammar, and E. Zegura,
“Agile virtualized infrastructure to proactively defend against cyber attacks,”
in IEEE INFOCOM,
April 2015.

\bibitem{changefinder}
J. Takeuchi and K. Yamanishi,
“A unifying framework for detecting outliers and change points from time series,”
IEEE Trans. Knowledge and Data Eng.,
vol. 18, no. 4, pp. 482-–492, 2006.

%\bibitem{globaldetector}
%T. Murase, Y. Fukushima, M. Kyobayashi, S. Nishimoto, R. Fujimaki, and T. Yokohira,
%“Performance evaluation of a multi-stage network event detection scheme against DDoS attacks,”
%in Proc. of APSITT, April 2008, pp. 56–63.

%\bibitem{as-rank}
%AS Rank, [Online]. Available: http://as-rank.caida.org.
\bibitem{albert2002statistical}
Albert, R{\'e}ka and Barab{\'a}si, Albert-L{\'a}szl{\'o},
"Statistical mechanics of complex networks,"
Reviews of modern physics, 74, 1, p. 47, 2002.


\bibitem{simpleweb}
Simple web pcap traces, [Online]. Available: http://www.simpleweb.org/wiki/traces/TCP-IP/location3/.

\end{thebibliography}
